# LaTeX Multi-Files Project Structure
---

### LaTeX __Source__ File Division
1. __Preamble__
    * Includes __\documentclass{class_name}__
    * Only LaTeX macros eg.packages 
1. __Body__
    * Includes __\begin{document}__
    * Text content with LaTeX Commands
    * Ends wih __\end{document}__
---
### General page order for __Thesis/Book/ProjectFile__
#### 1. FrontMatter 
    I. Half Title Page
    II. Title Page
    III. Copyright Page
    IV. Dedication
    V. Declaration
    VI. Acknowledgements
    VII. Abstract
    VIII. Table of Contents
    IX. List pf Figures
    X. List of Tables
    XI. List of Symbols / Notations
    XII. Preface
    XIII. Foreword
#### 2. Mainmatter
    a. Main Topic
    b. Appendix
#### 3. Backmatter
    a. Bibliography
    b. Glossary / Index
---

### Below are the __steps__ to create it:
1. Create __3__ directories i.e.
    a. __FrontMatter__
    b. __MainMatter__
    c. __BackMatter__
2. Now open your __LaTeX__ editor(in my case: TexMaker) & go to __main.tex__ where all file contect is stored.
3. Then simply create a new file & save it inside __MainMatter__ directory/folder. And cut-paste the content from __main.tex__ into this file.
_For-Example:_ 
    * __SCENARIO_1__: You cut-paste your _Introduction_ from __main.tex__ into this file.
    * __SCNEARIO_2__: You start cut-pasting your __Chapters__ from __main.tex__ into this file.
4. 


---
* #### Reference Video: [Youtube](https://www.youtube.com/watch?v=rLYdQf-G6vY "LaTeXFiles Organization")